%% CDC 2019
% *****************************************************

\input{0_abstract.tex}

\section{Background and contributions}
\input{1_introduction.tex}

\section{Embedded image-based control}~\label{sec:ch3_ProblemSetting}
\input{2_embeddedIBC.tex}
\section{\texorpdfstring{\Gls{ibc}}{IBC} model, mapping and configurations}~\label{sec:ch3_sys_model}
\input{3_systemModelling.tex}
\section{Control problem and \texorpdfstring{\gls{qoc}}{QoC} metrics}~\label{sec:ch3_control_problem}
\input{4_controlProblem.tex}
\section{Control design}~\label{sec:ch3_control_design}
The control design technique we choose decides the controller feedback and feedforward gains $\Kgain$ and $\Fgain$ for the control law defined in Section~\ref{sec:ch3_control law}. To design a controller, we assume that the sampling period $h_i$ and sensor-to-actuator delay $\tau_i$ are known.
\subsection{\Gls{mjls} synthesis}~\label{sec:ch3_MJLS}
\input{5_mjls.tex}
\subsection{\Gls{lqr} design with worst-case workload}~\label{sec:ch3_LQR}
We consider the system scenario for the worst-case workload $s_{wc}$ having the worst-case period and delay $(h_{wc},\tau_{wc})$ (one of the scenarios as explained in Section~\ref{sec:ch5_ch5_sys_scenario}) for designing the control law. The worst-case system scenario for the \gls{mjls} formulation is same as $s_{wc}$. We design a controller to minimize the following cost function
\begin{align}
J(u) = \sum\limits_{k=0}^{\infty} z[k]^Td_sC_{aug}^TC_{aug}z[k] + d_u^2|u[k]|^2,\nonumber
\end{align}
where $d_u,d_s \in \Real_{>0}$ represents the input weight and the state weights respectively. The weights are optimized for the considered \gls{qoc} metric. Typically, $d_u\ll d_s$ so as to optimise for control performance and $d_u\gg d_s$ to optimise for control energy (see Section~\ref{sec:ch3_observations}).
\subsection{Switched linear control design}~\label{sec:ch3_SPADe}
The switched linear control design we consider is explained in Section \ref{sec:ch5_embeddedIBC}. This is the basic principle used in the controller designs presented in Chapters \ref{chap:parallelisation} and \ref{chap:pipelined_parallelism}. Frequently occurring workload scenarios are characterised using the the PERT distribution. A set of optimal system scenarios are identified. \gls{lqr} controllers are designed for each of these scenarios $s_s$ with $(h_s,\tau_s)$ that minimises the cost function given in Section~\ref{sec:ch3_LQR}. Further, the stability of this switched system is analysed by deriving \glspl{lmi} that check for the existence of a \gls{cqlf}.

\section{Results, observations and guidelines}~\label{sec:ch3_Results}
\input{6_results.tex}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%Conclusion%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}~\label{sec:ch3_Conclusion}
We presented a \gls{mjls} formulation for controller synthesis for image-based control systems considering workload variations and platform implementation constraints.
Within the scope of \gls{spade}, we further compare this method with two relevant control paradigms: \gls{lqr} and switched linear control system design. 
We also provide design guidelines on the control technique to use for given constraints on the system knowledge, the \gls{qoc}, and the implementation.

The synthesis method assumes that the workload variations can be characterised as a \gls{dtmc}. A \gls{dtmc} is sensitive to the data used for its modelling. As a future work, sensitivity analysis of the \gls{dtmc} towards the \gls{qoc} needs to be evaluated. 
Further, the current design guidelines are provided based on multiple empirical simulation runs of the controller for varying workloads, number of scenarios, camera frame rate and given platform allocation. A formal mathematical analysis would strengthen our design guidelines. The challenge for a formal analysis of the control design is that we do not know the exact sequence of occurrence of the workload variations apriori.