\chapter{Introduction}%
\label{chap:intro}
\glsresetall

% \gls, \glspl, \Glspl, \acrlong{cpm}
Technology has been growing exponentially over the last few decades.
The constant evolution of computers, the internet, wireless telecommunication, smartphones, cameras, and other modern technologies are drastically transforming the world we perceive and are improving our standard of living.
If not for the cameras that captured my childhood days through photos and videos as memoirs, the world I grew up in would have been nothing but fiction for the current and future generations.
Nowadays, cameras have become an integral part of our daily lives - be it for taking selfies using our smartphone to post on social media or for collaborating with my colleagues over a video call.
Cameras, as sensors, have also become the "eyes" to perceive the surroundings for modern automotive systems, robots, autonomous systems and manufacturing systems.

\Gls{ibc} systems that use cameras as sensors, are increasingly popular due to their low-cost and high versatility. 
Cameras enable the perception of depth, relative position, geometry, relative distance, colour, and tracking of the object-of-interest. 
As such, \gls{ibc} systems are now an integral part of industrial \glspl{cps}.
\Glspl{cps} refer to a class of modern industrial systems with tight interaction between computation, communication and control elements (the cyber part), and physical processes such as motion, heating/cooling, vibration, wear and tear (the physical part) within these systems.
Designing \glspl{cps} requires an integrative design approach that allows for optimisation coping with the tight coordination between the cyber and the physical components~\cite{lee2008cyber,gunes2014survey,sanislav2012cyber}.
The \gls{ibc} system is compute-intensive and a standalone \gls{ibc} system behaves similar to a \gls{cps}.

This thesis focuses on optimising the design and implementation of \gls{ibc} systems in the resource-constrained \gls{cps} domain.
The case study used throughout this thesis is a \gls{lkas}, though the methods are directly applicable to similar systems in the \gls{cps} domain.
In this introductory chapter, first, the history of the camera and its modern significance are briefly explained.
Second, the context, definition and scope of \gls{ibc} systems are illustrated.
Then, an overview of the state-of-the-art is given and the research challenges with the contributions of this thesis are enumerated. 
After providing an overview of the design and optimization flow elaborated in this thesis, finally, the motivating case study and the thesis outline are detailed.

\input{01_intro/evolutionOfCamera}

\input{01_intro/ibc_systems}

\input{01_intro/platforms}

\input{01_intro/sota}

\input{01_intro/challenges_v2}

\input{01_intro/spade_overview}

\input{01_intro/lkas_case_study}


\section{Thesis outline}
This thesis is organized along the research challenges and scientific contributions outlined in Section \ref{chap:challenges}. Accordingly, the five scientific contributions are reported in Chapter \ref{chap:parallelisation} to Chapter \ref{chap:approximation}. 
Chapters \ref{chap:parallelisation}, \ref{chap:pipelined} and \ref{chap:pipelined_parallelism} focus on platform-aware design aspects where the research focus has been on reducing sampling period and delay by parallel implementation (Chapter \ref{chap:parallelisation}), pipelined implementation (Chapter \ref{chap:pipelined}) or their combination (Chapter \ref{chap:pipelined_parallelism}). Chapters \ref{chap:workloadVariations} and  \ref{chap:approximation} report design approaches exploiting application-specific characteristics. Chapter \ref{chap:workloadVariations} reports the proposed approach on dealing with workload variation in a sequential \gls{ibc} implementation. Chapter \ref{chap:approximation} presents the approximation-aware design of an \gls{ibc} system. It presents the \gls{imacs} framework for approximate computing in closed-loop systems. Chapter \ref{chap:concl} makes some concluding remarks and outlines a number of relevant future extensions. 

\vfill